Contextuality and Nonlocality in \\ Discrete Quantum Theory

### 2015-11-18 DQC3.tex
Update title and reference according to IOPLaTeXGuildines

\author{John Gardiner\\
 \affiliation{College of Physical and Mathematical Sciences, Brigham
  Young University, Provo, UT 84602, U.S.A}\\[.2in]
%% \author
Andrew J. Hanson\\
\affiliation{School of Informatics and Computing, Indiana University,
  Bloomington, IN 47405, U.S.A}\\[.2in]
%%\author
Gerardo Ortiz \\
\affiliation{Department of Physics, Indiana University, Bloomington, IN 47405,
U.S.A}\\[.2in]
%%\author
Amr Sabry\\
\affiliation{School of Informatics and Computing, Indiana University,
  Bloomington, IN 47405, U.S.A}\\[.2in]
%%\author
Yu-Tsung Tai\\
\affiliation{Department of Mathematics, Indiana University,
  Bloomington, IN 47405, U.S.A}\\
\affiliation{School of Informatics and Computing, Indiana University,
  Bloomington, IN 47405, U.S.A}}

@@

@@

\bibliographystyle{plain}
\bibliography{discreteGBKS}

>>>>

\author{John Gardiner$^{1}$, Andrew J. Hanson$^{2}$, Gerardo Ortiz$^{3}$,
Amr Sabry$^{1}$, Yu-Tsung Tai$^{42}$}

\address{$^{1}$ College of Physical and Mathematical Sciences, Brigham Young
University, Provo, UT 84602, U.S.A}

\address{$^{2}$ School of Informatics and Computing, Indiana University,
Bloomington, IN 47405, U.S.A}

\address{$^{3}$ Department of Physics, Indiana University, Bloomington, IN
47405, U.S.A}

\address{$^{4}$ Department of Mathematics, Indiana University, Bloomington,
IN 47405, U.S.A}

\ead{ortizg@indiana.edu}

@@

\submitto{\jpa}

@@

\section*{References}

\bibliographystyle{iopart-num}
\bibliography{discreteGBKS}
